### 2020-08-28 README.Rmd
avoid empty link
funding info as suggested by @cboettig

Note that `query_sources()` has found more locations than we have registered above.  This is because in addition to maintaining a local registry of sources, `contentid` registers online sources with the Hash Archive, <https://hash-archive.org>. (The Hash Archive doesn't store content, but only a list of public links at which content matching the hash has been seen.)  `query_sources()` has also checked for this content on the Software Heritage Archive, which does periodic crawls of all public content on GitHub which have also picked up a copy of this exact file. With each URL is a date at which it was last seen - repeated calls to `register()` will update this date, or lead to a source being deprecated for this content if the content it serves no longer matches the requested hash. We can view the history of all registrations of a given source using `query_history()`.  The [registries vignette]() provides more information on controlling which local and remote registries are searched and how these registries work.

@@

Any future calls to `resolve()` with this hash on this machine will then always be able to load the content from the local store.  This provides a convenient way to cache downloads for future use.  Because the local store is based on the content identifier, repeatedly storing the same content will have no effect, and we cannot easily overwrite or accidentally delete this content. For more on understanding and managing the local content store and other persistent storage options, see the [content store vignette]().

@@

>>>>

Note that `query_sources()` has found more locations than we have registered above.  This is because in addition to maintaining a local registry of sources, `contentid` registers online sources with the Hash Archive, <https://hash-archive.org>. (The Hash Archive doesn't store content, but only a list of public links at which content matching the hash has been seen.)  `query_sources()` has also checked for this content on the Software Heritage Archive, which does periodic crawls of all public content on GitHub which have also picked up a copy of this exact file. With each URL is a date at which it was last seen - repeated calls to `register()` will update this date, or lead to a source being deprecated for this content if the content it serves no longer matches the requested hash. We can view the history of all registrations of a given source using `query_history()`.

@@

Any future calls to `resolve()` with this hash on this machine will then always be able to load the content from the local store.  This provides a convenient way to cache downloads for future use.  Because the local store is based on the content identifier, repeatedly storing the same content will have no effect, and we cannot easily overwrite or accidentally delete this content.

@@

This work is funded in part by grant [NSF OAC 1839201](https://www.nsf.gov/awardsearch/showAward?AWD_ID=1839201&HistoricalAwards=false) from the National Science Foundation.
